### 2015-08-13 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
updated text

%%%
%%% SUBSECTION
%%%
\subsection{Motivation and Objectives}
\CO\; has been injected and stored in underground geological formations to dispose of acidic gasses (mainly H$_{2}$S and \CO) from industrial plants. This has helped to prove that geological \CO\; storage is a viable engineering and economic strategy for reducing GHG emissions. However, geological CO2 storage schemes must comply with requirements (European Council's directive 2009/31/EC) for:
\begin{enumerate}[(a)]
   \item Site screening and selection to identify potential geological locations for \CO\; storage;\label{options:a}
   \item Site characterisation to assess the engineering and economic feasibility;\label{options:b}
   \item Simulation of potential injection strategies to assess (i) pressure and stress distribution and their evolution in time, (ii) plume migration, (iii) oil recovery, (iv) storage capacity and (v) flow rate of injection;\label{options:c}
   \item Risk assessment to identify risks of leakage via pathways identified in (~\ref{options:c}), to design a monitoring scheme for continuous assessment of these risks, and to develop contingency plans in case of  leakage scenarios;\label{options:d}
   \item Site management and operation to ensure that the site is operated in compliance with regulations and to continuously assess the risks associated with the storage site during operation, closure and post-closure stages.\label{options:e} 
\end{enumerate}

@@

\begin{comment}

%%%
%%% ABSTRACT (100 words)
%%%
\section{Abstract}

{\it Abstract: A 100 word synopsis of the proposed research project suitable for the lay reader.}

Motivation:

Objective:

Brief Description:

Expected Outcome:

%%%
%%% Why the Levehulme Trust (250 words)
%%%
\section{Why the Levehulme Trust}

Why the Leverhulme Trust?: It is in the Principal Applicant's interests to ensure that a full clear justification for applying to the Trust is provided, based on their understanding of the character of the Trust. Peer reviewers and Trust Board members place considerable weight on your reply, so give very careful thought to what you write and take note of the following six tips:
• Consult “Our approach to grant making” on the Trust’s website to determine if your project fits the type of research we are seeking to fund.
• Do not simply cut and paste text from our website – we know what our own website says!
• Do not just repeat what you have said elsewhere on the application form – duplicating information is not a good use of the space.
• Do answer the question. Don’t use the space to say something not relevant to the question.
• Avoid writing purely descriptive text about the research project or about the skills of the research team. You can address these points elsewhere in the application.
• Consider carefully whether the Trust really is the best recipient for your application – it may be that other funders are more suitable for the type of research you wish to undertake.

%%%
%%% Other Research Commitments (50 words)
%%%
\section{Other Research Commitments}

Other Research Commitments: This information is required to enable assessors to judge whether the Principal Applicant will have sufficient time available to devote to the proposed project.

%%%
%%% Summary of the Proposal (1000 words)
%%%
\section{Summary of the Proposal}

Proposal Summary: The summary should be written in a style suitable for a reader with good knowledge of the subject area. It should include hypotheses to be tested, objectives, significance, methods to be used, and details of how results will be published.
The upload limit is two pages (ARIAL 11). You can include figures but may need to add these in a table for formatting reasons. The system does not suppport PDFs. The word limit for text entry is 1000.

%%%
%%% References (500 words)
%%%
\section{References}

References: If applicable please provide a bibliography for the proposal summary.
Please note that the maximum file size for an uploaded document is 2MB.

%%%
%%% Co-Applicants
%%%
\section{Co-Applicants}
A maximum of 3 co-applicants can be added.
Co-applicants can be from a non-UK institution - and will be asked to confirm their participation in the project before it can be submitted to the Trust. It is the Principal Applicant's responsibilty to ensure that any co-applicants are aware of their role in the application process. Should the application proceed to the Detailed Application stage,they should complete their CV details within their own account and approve the application before it can be submitted - applicant's are responsible for making the necessary arrangements with their co-applicants.
Please note co-applicants may not claim a salary from the Trust, therefore they can not be the named researcher/ student on the proposal. Replacement teaching costs can be added for the Co-Applicants. To be eligible for these, they must be currently employed on a continuing basis by their eligible institution. A maximum of one year’s (33$\%$) staff replacement per grant over the course of a three year grant may be awarded – and pro rata for grants of different lengths or for those with contracts less than full time, e.g up to 8 months for a two year grant, up to 16 months for a four year grant, and so on. The replacement should not be someone currently studying for a research degree. The staff replacement should normally start at the most junior point of the lecturer scale of the institution concerned. Replacement teaching is not allowable for co-applicants outside of the UK.

%%%
%%% Referees
%%%
\section{Referees}

The individuals should be able to provide the Trust with an independent opinion on the proposed project at the detailed application stage. They must not themselves be closely allied with the project, and must be located in institutions other than that of the Principal/ Co Applicant(s).
Referees are not allowed to come from the same institution as each other. Referees based overseas are acceptable. You will need to enter complete details, including a department. Enter N/A if not applicable.
It is the responsibility of the Principal Applicant to ensure that these individuals will be in a position to respond promptly to the Trust should the proposal progress to the Full Application stage.

%%%
%%% RESEARCH GRANTS
%%%
\section{Previous and Current Research Grants}

RESEARCH PROJECT GRANTS $\&$ INTERNATIONAL NETWORKS
Previous/current application to the Leverhulme Trust: Please provide details of the Principal Applicant’s applications to the Leverhulme Trust.  If none, please enter None or N/A in the title box.
Previous/current application to other funding bodies: Please provide details of current or recent applications of Principal Applicant to other bodies for identical or closely related projects with dates and results. Please comment on reasons for rejection if known.  If none, please enter None or N/A in the title box.
INTERNATIONAL NETWORKS ONLY
Abstract: Please provide a summary of current or recent applications to other funding bodies in other subject areas. Please comment on reasons for rejection if known.
Title: character limit of 50
Ref No: character limit of 10

%%%
%%% FINANCE
%%%
\section{Finance}
Salary budget:  It is recommended that you liaise with your institution regarding the budget to minimise any delays. 
One Research Assistant, Local Researcher or PhD Student must spend at least 50% of their time on the project - of all of the time.
When entering the ‘Percentage of time spent on the project’ please ensure that you enter the percentage of time over the entire project duration, not for each year – for research assistants, PhD students and local researchers.
Personal details such as First name, Surname, Title and Current employment only need to be entered if known at time of application. However, if you do tick Name Known, personal details will become mandatory.

The Trust does not make awards on a full economic costing basis.
The budget should be entered in £ sterling.
Every field should be completed using zeros where necessary. Do not include pence.

A local researcher is where the research is taking place outside the UK and it is more appropriate to employ personnel local to the area than a UK based person paid to travel to the region.
A consultant is for use when someone is required for a limited number of hours across the duration of the project. This is not for the provision of a salary for a consultant.
Replacement teaching can be added for the Principal/Co-Applicants. To be eligible for these, applicants must be currently employed on a continuing basis by their eligible institution. A maximum of one year’s replacement per grant over the course of a three year grant – and pro rata for grants of different lengths or for those with contracts less than full time – may be awarded. The replacement should not be someone currently studying for a research degree. The staff replacement should normally start at the most junior point of the lecturer scale of the institution concerned.
Explicit and clear justification should be provided for why replacement teaching costs are sought/required. Do not simply provide a breakdown of how this is calculated, but why this is required for the project.
Associated costs: Please be reminded that the total Associated Costs cannot exceed 25$\%$ of the total amount requested.  Select type from drop down list.  Please choose only ONE of each type, and total specific items within the type, fully detailing and justifying the cost within the justification box.
Open Access costs are permissible and should be included within the 25$\%$ associated costs allowable However, open access charges should only be incurred during the period of a Leverhulme award (rather than being built into a budget but with anticipated expenditure after the research and award has concluded).  If these costs are not incurred during the life of the grant, the funds cannot be switched to any other budget heading, and must be returned to the Trust.

%%%
%%% SECTION
%%%
\section{Track Record}

%%% 
%%% SECTION
%%%
\section{Case for Support}

%%%
%%% Sub-Section
%%%
\subsection{Motivation and Objectives}
\begin{itemize}
\item \red{1-2 Paragraphs on general motivation for the proposed project}
\item \red{1-2 Paragraph on applications or how the project will benefit power generation via geothermal energy developments and  hydrocarbon production in HPHT reservoirs} 
\end{itemize}

Furthermore, because of the high pressures involved, the injection of cold fluids into the geothermal reservoir (at high temperature and pressure conditions) may lead to the formation of further stress- and thermal-induced fractures. \blue{Text linking injection to isenthalpic flash}.

 Within this context, the research proposed here is aimed at developing an integrated model framework to investigate CO$_{2}$-brine-contaminants flows in thermal energy recovery systems in geological formations at high temperature and pressure conditions. The ultimate goal is to be able to improve our understanding of density- and viscous-driven fluid instabilities in liquid-vapour fronts.

 experimentally validating comprehensive predictive models for both dense phase pneumatic conveying and fluidized bed gasifiers, which fully represent the physics of particulate behaviour (in its production, transport and interaction at a surface). The ultimate objective is to be able to design coal gasifiers in which these aspects can be controlled in such a way as to deliver a further increase in thermal efficiency of around 5%, leading to a further decrease in CO2 emissions of 10% per kWh. Modelling is essential as real scale, actual pressure/temperature experiments are inordinately expensive. This will require both experimental and computational elements. The former will provide information at a level of detail and at conditions hitherto not available. The objectives of this 48 month project are:

%%%
%%% Sub-Section
%%%
\subsection{Technical Background -- Coupled Non-Equilibrium Vapour-Liquid Equilibria and Transport of Volatile Organic Geochemicals }

%%%
%%% Sub-Section
%%%
\subsection{Methodology and Work Programme}

%%%
%%% Sub-Section
%%%
\subsection{Impact Summary}

%%%
%%% Sub-Section
%%%
\subsection{Academic Beneficiaries}

%%%
%%% SECTION
%%%
\section{Justification of Resources}

%%%
%%% SECTION
%%%
\section{Pathways for Impact}

%%%
%%% SECTION
%%%
\section{Workplan}

>>>>

%%%
%%% SUBSECTION
%%%
\subsection{Motivation and Objectives}
\CO\; has been injected in underground geological formations to enhance hydrocarbon productivity (e.g. \CO-EOR) whilst disposing acidic gasses (mainly H$_{2}$S and \CO) from natural occurance or captured from industrial plants. This has helped to prove that geological \CO\; storage is a viable engineering and economic strategy for reducing GHG emissions. However, geological \CO\; storage schemes must comply with requirements (European Council's directive 2009/31/EC) for:
\begin{enumerate}[(a)]
   \item Site screening and selection to identify potential geological locations for \CO\; storage;\label{options:a}
   \item Site characterisation to assess the engineering and economic feasibility;\label{options:b}
   \item Simulation of potential injection strategies to assess (i) pressure and stress distribution and their evolution in time, (ii) plume migration, (iii) oil recovery, (iv) storage capacity and (v) flow rate of injection;\label{options:c}
   \item Risk assessment to identify risks of leakage via pathways identified in (~\ref{options:c}), to design a monitoring scheme for continuous assessment of these risks, and to develop contingency plans in case of  leakage scenarios;\label{options:d}
   \item Site management and operation to ensure that the site is operated in compliance with regulations and to continuously assess the risks associated with the storage site during operation, closure and post-closure stages.\label{options:e} 
\end{enumerate}

@@
